---
title: "LIWC"
output: html_document
---

### Import Packages
```{r}
library(tidyverse)
library(ggpubr)
library(rstatix)
library(car)
library(GGally)
```


### Read Data
```{r}
dataset = read.csv(file="liwc.csv",head=TRUE)
dataset$sex = as.factor(dataset$sex)
dataset =dataset %>% mutate_if(is.integer,as.double)
names(dataset)[names(dataset)=='sex']='gender'
summary(dataset)
```
### Visualization of Data group by Gender
```{r}
png(file="liwc-A.png",
width=600, height=350)
ggboxplot(
  dataset, x = "gender", y = colnames(dataset)[1:10], ylab = "word count",
  merge = TRUE, palette = "jco"
  )
dev.off()
png(file="liwc-B.png",
width=600, height=350)
ggboxplot(
  dataset, x = "gender", y = colnames(dataset)[11:20], ylab = "word count",
  merge = TRUE, palette = "jco"
  )
dev.off()

png(file="liwc-C.png",
width=600, height=350)
ggboxplot(
  dataset, x = "gender", y = colnames(dataset)[21:30], ylab = "word count",
  merge = TRUE, palette = "jco"
  )
dev.off()

png(file="liwc-D.png",
width=600, height=350)
ggboxplot(
  dataset, x = "gender", y = colnames(dataset)[31:40], ylab = "word count",
  merge = TRUE, palette = "jco"
  )
dev.off()

png(file="liwc-E.png",
width=600, height=350)
ggboxplot(
  dataset, x = "gender", y = colnames(dataset)[41:48], ylab = "word count",
  merge = TRUE, palette = "jco"
  )
dev.off()
```


### Multivariate Normality Test
```{r}
library("MVN")
par(mar=c(2.1,2.1,2.1,2.1),mgp=c(1,0.25,0))
# par(adj)
result = mvn(data = dataset, subset = "gender", mvnTest = "hz",
univariateTest = "AD", univariatePlot = "histogram",
multivariatePlot = "qq", multivariateOutlierMethod = "adj",
showOutliers = TRUE, showNewData = TRUE)
```

### Remove variables that does not look like Normally distributed
```{r}
dataset = subset(dataset, select=-c(Netspeak,Informal.language,Biological.processes,Negative.emotion,X1st.Person.Singular.Pronoun))
```


### Find and remove outliers
```{r}
dataset %>%
  group_by(gender) %>% 
  mahalanobis_distance() %>%
  filter(is.outlier==TRUE) %>%
  as.data.frame()


dataset.outlierf = dataset %>%
  group_by(gender) %>% 
  mahalanobis_distance() %>%
  ungroup() %>%
  as.data.frame()
  

dataset.outlierf$gender = dataset$gender
dataset.outlierf = dataset.outlierf %>%
  filter(is.outlier==FALSE) %>%
  select(-c(is.outlier,mahal.dist))


```

### Identify multicollinearity
```{r}
dataset[-length(dataset)] %>% cor_test() %>% filter(p>0.05)
```


### Check linearity assumption
```{r}

results = dataset %>%
  group_by(gender) %>%
  doo(~ggpairs(.) + theme_bw(), result = "plots")
results$plots
```

### Check the homogneity of variance assumption

```{r}
dataset %>% 
  gather(key = "variable", value = "value", -gender) %>%
  group_by(variable) %>%
  levene_test(value ~ gender) %>%
  filter(p<0.05)
```

### Check the homogeneity of covariances assumption
```{r}
box_m(dataset[-length(dataset)],dataset$gender)
```


### Perform MANOVA

```{r}
dvar = data.matrix(dataset[-length(dataset)])
model = lm(dvar ~ gender, dataset)
summary(Manova(model, test.statistic = "Pillai"))

```

```{r}
library(effectsize)
manova_model= manova(model)

eta_squared(manova_model)
```

```{r}
summary(manova_model)
```


### POST HOC

### Compute univariate one-way ANOVA: welch ANOVA

```{r}
alpha = 0.05/(length(dataset)-1)
welch = dataset %>% 
  gather(key = "variable", value = "value", -gender) %>%
  group_by(variable) %>%
  welch_anova_test(value ~ gender)%>%
  select(-c(.y.,n,method))


```


### Compute univariate one-way ANOVA: ANOVA

```{r}
alpha = 0.05/(length(dataset)-1)
dataset %>% 
  gather(key = "variable", value = "value", -gender) %>%
  group_by(variable) %>%
  anova_test(value ~ gender) %>%
  as.data.frame() %>%
  filter(p>alpha)

  
```
### Compute multiple pairwise comparisons: Games Howell

```{r}
dataset %>% 
  gather(key = "variable", value = "value",-gender) %>%
  group_by(variable) %>%
  games_howell_test(value ~ gender) %>%
  select(-estimate, -conf.low, -conf.high) %>%
  filter(p.adj>0.05)
# Remove details
```
### Compute multiple pairwise comparisons: pairwise_t_test

```{r}

dataset %>% 
  gather(key = "variable", value = "value",-gender) %>%
  group_by(variable) %>%
  pairwise_t_test(value ~ gender, pool.sd = FALSE , var.equal = FALSE) %>%
  
  filter(p.adj>0.05)


```

### Check the homogneity of variance assumption: Without Outlier

```{r}
dataset.outlierf %>% 
  gather(key = "variable", value = "value", -gender) %>%
  group_by(variable) %>%
  levene_test(value ~ gender) %>%
  filter(p<0.05)
```
### Check the homogeneity of covariances assumption: Without Outlier

```{r}

box_m(dataset.outlierf[-length(dataset.outlierf)],dataset.outlierf$gender)
```


### Perform MANOVA: Without Outlier


```{r}
dvar = data.matrix(dataset.outlierf[-length(dataset.outlierf)])
model1 = lm(dvar ~ gender, dataset.outlierf)
Manova(model, test.statistic = "Pillai")

```

```{r}
manova_model= manova(model1)

eta_squared(manova_model)
```


### POST HOC: Without Outlier

### Compute univariate one-way ANOVA: welch ANOVA

```{r}
alpha = 0.05/(length(dataset.outlierf)-1)
dataset.outlierf %>% 
  gather(key = "variable", value = "value", -gender) %>%
  group_by(variable) %>%
  welch_anova_test(value ~ gender) %>%
  filter(p>alpha)
```

### Compute univariate one-way ANOVA: ANOVA

```{r}
alpha = 0.05/(length(dataset.outlierf)-1)
dataset.outlierf %>% 
  gather(key = "variable", value = "value", -gender) %>%
  group_by(variable) %>%
  anova_test(value ~ gender) %>%
  as.data.frame() %>%
  filter(p>alpha)

  
```
### Compute multiple pairwise comparisons: Games Howell

```{r}
dataset.outlierf %>% 
  gather(key = "variable", value = "value",-gender) %>%
  group_by(variable) %>%
  games_howell_test(value ~ gender) %>%
  select(-estimate, -conf.low, -conf.high) %>%
  filter(p.adj>0.05)
# Remove details
```
### Compute multiple pairwise comparisons: pairwise_t_test

```{r}

dataset.outlierf %>% 
  gather(key = "variable", value = "value",-gender) %>%
  group_by(variable) %>%
  pairwise_t_test(value ~ gender, pool.sd = FALSE , var.equal = FALSE) %>%
  filter(p.adj>0.05)
# Remove details

```